Interisland movements and oceanic swimming of woodland caribou in Newfoundland

### 2020-05-14 paper/manuscript.Rmd
Q5

5) In relation to all the previous questions: how do individuals vary in their
assessment of the costs and benefits of swimming between islands? Why did some
caribou regularly engage in swimming events, while more than half of our marked
population were never observed swimming in the ocean? The forage limitation
hypothesis is thought to apply uniformly across populations, but
individual caribou could evaluate the costs and benefits of swimming to another
island differently. It is possible that some individuals, in our case ~10%,
considered swimming to be less costly or perceived competition or predation more
acutely than their conspecifics.

>>>>

5) In relation to all the previous questions: how do individuals vary in their
assessment of the costs and benefits of swimming between islands? Why did some
caribou regularly engage in swimming events, while more than half of our marked
population were never observed swimming in the ocean? The forage limitation
hypothesis is thought to apply uniformly across populations, but individual
caribou could evaluate the costs and benefits of swimming differently. It is
possible that some individuals, in our case ~10%, considered swimming to be less
costly or perceived competition or predation more acutely than their
conspecifics.
